Wetting of the tarsal adhesive fluid controls underwater adhesion in ladybug beetles

### 2021-05-07 source/tex/ladybug_adhesion.tex
referee 1 further comments included to MS

The goal of this paper is to provide a generalised picture of adhesion in insects which use hairy pads and secrete an oily fluid for attachment. We used the ladybug beetle (\emph{Coccinella septempunctata}) as an animal model to first experimentally measure adhesion force of its individual pads in air and underwater conditions, both on smooth hydrophilic and hydrophobic glass surfaces. We further tested whether the chemical profile of the adhesive fluid changes when the hairs were submerged in water. Second, we developed a simple theoretical model considering capillary forces to predict the net adhesion force of a hairy pad under different conditions. The case of underwater adhesion was studied both in the presence and absence of a trapped bubble, to decouple the bubble's role in the insect's adhesion. Finally, we
discuss key insights gained from our experiments and model with regards to understanding adhesion in other animals.

@@

The seven-spotted male adult ladybug beetles (\emph{Coccinella septempuctata})
were purchased from Katz Biotech (Baruth, Germany) and housed in a plastic box filled with leaves,
twigs and stones at room temperature and 60-80\% relative humidity
with daily access to sunlight. They were fed with raisins, honey and
water \emph{ad libitum}.

 %The beetle's leg was constrained similar to the method described by Bullock et al \cite{RN19}.
An individual beetle was first carefully anaesthetised using small amounts of CO\textsubscript{2} sublimating
from a piece of dry ice and then glued with a small dollop of epoxy glue on its elytra to the underside of a heavy steel ball. The ball was held in a bracket which allowed free rotational movement of the ball in each direction, thus helping to align the suspended beetle over the substrate (see Fig.~\ref{fig:Setup}). The bracket with the ball and the beetle could be further positioned by manual micro-manipulators in all three axes before the experiments. One front left leg was carefully fixed to a piece of soft solder wire coming off the steel ball using Blu Tack (Bostik Ltd., U.K.) allowing us to further align the leg to the substrate. The claws on the leg were also fixed to the wire using epoxy glue to prevent any further wiggling and to prevent the claws from touching the substrate. Care was taken to ensure the glue doesn't contaminate the pads. Each leg of a male ladybug beetle has two pads. For the test, we only allowed the distal pad to come into contact with the substrate thus minimising partial or bad contact of the other one. A small piece of non-sticky Teflon tape helped to keep other legs tucked close to the body and avoided any interference during the adhesion test. After the measurements, the beetle was freed by carefully removing the epoxy glue and Blu Tack without harming it and set free.

@@

Adhesion measurements were performed on a custom force measurement
setup developed in-house (Figure \ref{fig:Setup}). A fibre optic
displacement sensor (\emph{Philtec D20, PHILTEC, Inc. USA}) together
with a steel bending beam (spring constant = 68.1 N/m) constitutes
the vertical force sensor. Beam deflection was calibrated using 4
different known weights to get the corresponding force. A plastic
3D printed substrate holder was glued to the end of the bending beam.
The holder was designed to enable switching from one substrate to
another without removing any glue. It also had transparent side walls
which allowed us to fill it with water for the underwater experiments
as well as observe the contact. The force sensor was mounted on a stage
consisting of a X-piezo element, used for precise lateral movements. Additionally, a separate Z-piezo element, fixed upright,
was used for vertical up-down motion, bringing the insect in contact
with the substrate from the top. Coarse movements of the bottom stage were done using the XYZ motors.
A coaxial illuminated tube microscope
(\emph{Navitar}) with 2$\times$ objective and a stereo-microscope
with 1$\times$ objective (\emph{Wild Heerbrugg}) fit with digital video cameras (\emph{FLIR Blackfly S}, 2448 x 2048 px; \emph{Basler ace U}, 1280 x 1024 px)
were used to record the sample contact with the substrate from ventral
and side views respectively. Pad contact area was visualised through
the substrate under reflection mode with the help of co-axial illumination. A goniometer was used to adjust the substrate alignment
with the ventral view optics to achieve total internal reflection.
The data acquisition from the force sensor and cameras, together with
the appropriate piezo motion steps were synchronised using a custom
LABVIEW program. Force data was acquired at a sample rate of 984 Hz,
averaged to 512 points per motion step. Videos were recorded at 20
frames per second.

The vertical and lateral piezos were used together to perform approach-retract
adhesion tests with the substrate to get the pull-off force. However,
instead of a simple down-up motion, an additional 100 \textmu m lateral sliding motion was introduced after the leg made contact, to ensure most of the hair tips align well with the substrate \cite{RN19}.
A further 10 \textmu m compression step (approach) set all hairs in slight compression which helped further contact
with the surface. Next, a short pause (1 s) removed any
viscoelastic effects before finally retracting the leg away from the
substrate. All approach, retract and lateral slide motion was done
at a speed of 62.5 \textmu m/s. Ventral view video recordings
were used for contact area extraction while the side view imaging
was used to visually aid orienting the pad with the substrate before
a test.

For underwater experiments, 1 ml Milli-Q water was pipetted into the
substrate holder. In order to achieve an underwater contact without
a trapped air bubble, the water was first degassed in a vacuum chamber
at 10 mbar pressure for 3 hours and used immediately. Before the experiments,
the pad was brought into contact with the dry surface 10 times repeatedly 
to equilibrate the pad's secretion system.

Five force measurements were subsequently performed on a fresh spot of the substrate and averaged for data analysis. Experiments were repeated with five individual beetles for each type of contact and substrate. In total, 30 beetles were tested.

@@

For measurements in air, the pull-off force was defined as the minimum
negative force during the final retraction step (Figure \ref{fig:Setup}).
For underwater measurements, an additional correction was necessary.
When the beetle was partially submerged underwater, its contact line at the
water surface shifted, which influenced the force readout due to surface
tension and buoyancy. This effect needed to be cancelled. So, a ``background''
force data was recorded, where the submerged beetle makes no contact
with the substrate. This background data was then subtracted from
a typical force data with substrate contact to correct for the external
surface tension effects. The pull-off force was subsequently calculated
from the minima as before.

@@

Standard 20 mm wide glass cover-slips were used as the hydrophilic
substrate. Glass was wiped with isopropanol, rinsed in water and dried
under nitrogen flow. The surface was then plasma cleaned in a oxygen
plasma chamber (Diener Electronic Femto) for 10 min at 120 W. The
surface was further rinsed with water and dried under nitrogen flow.

For the hydrophobic substrate, the glass cover slip was coated with
a fluorosilane via chemical vapour deposition (CVD). First, the glass
was cleaned using IPA and plasma treated as before. Next, 0.2 ml of
Trichloro(1H,1H,2H,2H-perfluorooctyl) silane (PFOTS), procured from
Sigma Aldrich, was put in a sealed chamber along with the the cleaned
glass. The chamber was placed under 100 mbar pressure for 10 min for
the CVD process. Finally, the substrate was annealed at 150\textcelsius{}
for 3 hours.

The substrate wetting was characterised by dynamic contact angle
measurements, performed with a DataPhysics OCA 35 contact angle goniometer.
Milli-Q water and n-hexadecane were used as test liquids. Advancing
and receding contact angles were measured for a maximum drop volume
of 10 \textmu l and with 0.5 \textmu l/s flow rate.

\begin{table}[H]
\centering{}%
\begin{tabular}{|c|c|c|c|}
\hline 
Substrate & Liquid & \ensuremath{\theta}\textsubscript{A} & \ensuremath{\theta}\textsubscript{R}\tabularnewline
\hline 
\hline 
\multirow{2}{*}{Glass} & Water & 63\ensuremath{\pm}5\textdegree{} & 20\ensuremath{\pm}2\textdegree{}\tabularnewline
\cline{2-4} \cline{3-4} \cline{4-4} 
 & n-Hexadecane & <10\textdegree{} & <10\textdegree{}\tabularnewline
\hline 
\multirow{2}{*}{PFOTS} & Water & 122\ensuremath{\pm}1\textdegree{} & 93\ensuremath{\pm}2\textdegree{}\tabularnewline
\cline{2-4} \cline{3-4} \cline{4-4} 
 & n-Hexadecane & 88\ensuremath{\pm}2\textdegree{} & 56\ensuremath{\pm}5\textdegree{}\tabularnewline
\hline 
\end{tabular}\caption{Dynamic contact angles measurements \label{tab:Contact-Angles}}
\end{table}

\subsubsection{Field desorption mass spectroscopy}

A previous study on arachnids \cite{RN223} reported that its secreted
fluid does not dissolve in water. To test whether the beetles retain
their adhesive fluid underwater unchanged, we performed a Field Desorption Mass Spectroscopy
(FDMS) using a ZAB 2-SE-FPD spectrometer (VG Instruments). The measurements
were done on the extracted secretions before and after rinsing its
legs with water. The middle leg of an Asian ladybird (\emph{Harmonia
axyridis}) was immersed in 50 \textmu L THF for 20 min and then transferred
to the measurement chamber of the FDMS. As a reference, pure THF was
used. The second middle leg of the same ladybird was subsequently
immersed in 100 \textmu L Milli-Q water for 15 min, then in THF for
20 min and then transferred to the measurement chamber of the spectrometer.
Molecular composition was extracted from the peak positions of the
FDMS spectra.

@@

\subsubsection{Adhesion measurements}

@@

\begin{figure}[H]
\centering{}\includegraphics[scale=0.5]{Figure2-Expt_effect_of_contact}\caption{\label{fig:Effect-of-contact}Box-and-whisker plot showing single
leg adhesion force measurements of ladybug beetle (\emph{Coccinella
septempuctata}) on glass and PFOTS substrates in air and underwater
conditions. The two modes of contact during underwater experiments
are represented separately: \textquotedblleft\emph{bubble}\textquotedblright{}
and \textquotedblleft\emph{no bubble}\textquotedblright . Crosses
represent theoretical predictions of adhesion force, while, circles
represent the contribution of the bubble itself, calculated from the
capillary bridge model. In the model, hair diameter = 4 \textmu m,
pad diameter = 200 \textmu m, hair height = 40 \textmu m,
N\protect\textsubscript{hairs} = 500, V\protect\textsubscript{fluid}
= 4.2 fL and V\protect\textsubscript{bubble} = 1.2 nL. Interfacial
tension of the adhesive fluid in air and water were assumed to be
24 mN/m and 48 mN/m respectively and water surface tension is 72 mN/m.}
\end{figure}

Apart from the three depicted contact types, we observed an additional
fourth type which occurred in roughly 25\% of our underwater experiments.
In this scenario, the ventral view recordings show that the hairs
did not appear to contact well with the substrate, unlike the other
three contact types. This ``bad contact'' scenario shows no adhesion
with either glass or PFOTS substrate. While it was not completely
clear why such a contact occurs, there can be two possible reasons.
First, the hairs could get bundled due to a small air meniscus within
the hairs, resulting in their disorientation. Second, a thin water
layer at the substrate interface might not be drained out to allow
the hairs to make contact with the substrate, resulting in a loss
of adhesion.

\subsubsection{Field desorption mass spectroscopy}

FDMS results confirm the presence of adhesive fluid on an Asian ladybird's
leg when underwater (Table \ref{tab:Molecular-distribution-of}).
Molecular weights of the secreted fluid mixtures extracted from the
beetle's leg, without and after immersion in water, show that, except
for two molecular weights (406.8 g/mol and 331.6 g/mol), the chemical
fingerprint remained unchanged. This indicates that the adhesion fluid
was not washed away underwater. Probable compounds in the fluid, corresponding
to the resultant molecular weights, include mostly aliphatic hydrocarbons
with traces of aldehydes. Our preliminary measurements on \emph{Harmonia axyridis} gives us confidence
to assert that, even for the case of \emph{Coccinella
septempuctata}, the adhesive fluid was not washed away from the hairs during the underwater experiments.

\begin{table}[H]
\centering{}%
\begin{tabular}{|c|c|c|}
\hline 
Without rinsing (g/mol) & After rinsing (g/mol) & Probable compounds\tabularnewline
\hline 
\hline 
324.5 & 324.5 & C\textsubscript{23}H\textsubscript{48}, C\textsubscript{22}H\textsubscript{44}O\tabularnewline
\hline 
 & 331.6 & C\textsubscript{24}H\textsubscript{44}\tabularnewline
\hline 
350.5 & 350.5 & C\textsubscript{25}H\textsubscript{50}\tabularnewline
\hline 
352.5 & 352.5 & C\textsubscript{25}H\textsubscript{52}, C\textsubscript{24}H\textsubscript{48}O\tabularnewline
\hline 
378.5 & 378.5 & C\textsubscript{27}H\textsubscript{54}\tabularnewline
\hline 
404.6 & 404.5 & C\textsubscript{29}H\textsubscript{56}\tabularnewline
\hline 
406.8 &  & C\textsubscript{29}H\textsubscript{58}\tabularnewline
\hline 
432.8 & 432.7 & C\textsubscript{31}H\textsubscript{60}\tabularnewline
\hline 
\end{tabular}\caption{Molecular weights of adhesive fluid secretion of \emph{Harmonia axyridis}
with and without rinsing the beetle's leg in water. \label{tab:Molecular-distribution-of}}
\end{table}

@@

\begin{figure}[H]
\includegraphics[width=0.7\linewidth]{Figure3-Model_schematic}\caption{\label{fig:Model}The capillary bridge model. The hairs make contact
with the substrate in three ways: a) \emph{In air}, where the adhesive
fluid bridges are surrounded by air; b) \emph{Underwater: no bubble},
where the adhesive fluid bridges are fully surrounded by water; c)\emph{
Underwater: bubble}, where part of the adhesive fluid bridges are
inside the bubble while others are outside in water. The corresponding
ventral view contact images of the beetle's pad are shown on the right.}
\end{figure}

@@

Our study provides further validation that capillary forces govern insect adhesion and van der Waals contribution,
if any, must be negligible. Further, the capillary forces can even
enable insect attachment underwater depending on the substrate chemistry.
When underwater, without a trapped bubble, the pads adhere strongly
to a hydrophobic substrate, but poorly to a hydrophilic substrate,
even though it shows similarly strong adhesion to both substrates
in air. This behaviour can only be explained by capillary forces and the wetting properties of the fluid. Our
preliminary FDMS results further provides validation to our assumption
that the adhesive fluid can form capillary bridges with the substrate
in water, instead of getting washed away (Table \ref{tab:Molecular-distribution-of}).

>>>>

The goal of this paper is to provide a generalised picture of underwater adhesion in insects which use hairy pads and secrete an oily fluid for attachment. We used the ladybug beetle (\emph{Coccinella septempunctata}) as an animal model to first experimentally measure adhesion force of its individual pads in air and underwater conditions, both on smooth hydrophilic and hydrophobic glass surfaces. Male ladybug beetles were chosen since they possess adhesive pads having mostly flat discoidal tipped hairs, which allow them to show superior adhesion on hard surfaces compared to females \cite{RN145}. Second, we developed a simple theoretical model considering capillary forces to predict the net adhesion force of a hairy pad under different conditions. The case of underwater adhesion was studied both in the presence and absence of a trapped bubble, to decouple the bubble's role in the insect's adhesion. Finally, we
discuss key insights gained from our experiments and model with regards to understanding adhesion in other animals.

@@

The seven-spotted adult male adult ladybug beetles (\emph{Coccinella septempuctata})
were purchased from Katz Biotech (Baruth, Germany). The beetles were housed in a plastic box filled with leaves,
twigs and stones at room temperature and 60-80\% relative humidity
with daily access to sunlight. They were fed with raisins, honey and
water \emph{ad libitum}. The beetles on average weighed 34 $\pm$ 4 mg and were experimented on within three weeks of being housed under above conditions.

 %The beetle's leg was constrained similar to the method described by Bullock et al \cite{RN19}.
An individual beetle was first carefully anaesthetised using small amounts of CO\textsubscript{2} sublimating
from a piece of dry ice and then glued with a small dollop of epoxy glue on its elytra to the underside of a heavy steel ball. The ball was held in a bracket which allowed free rotational movement of the ball in each direction, thus helping to align the suspended beetle over the substrate (see Fig.~\ref{fig:Setup}). The bracket with the ball and the beetle could be further positioned by manual micro-manipulators in all three axes before the experiments. One front left leg was carefully fixed at its tibia to a piece of soft solder wire coming off the steel ball using Blu Tack (Bostik Ltd., U.K.), allowing us to further align the leg to the substrate. Each leg of a male ladybug beetle has two hairy adhesive pads. For the test, we only allowed the distal pad to come into contact with the substrate thus minimising partial or bad contact of the other one. The distal pad was thus restrained by fixing its dorsal side to the wire using Blu Tack. The claws on the leg were also fixed to the wire using epoxy glue to prevent any further wiggling and to prevent the claws from touching the substrate. Care was taken to ensure the glue doesn't contaminate the rest of the tarsomeres. A small piece of non-sticky Teflon tape helped to keep other legs tucked close to the body and avoided any interference during the adhesion test. After the measurements, the beetle was freed by carefully removing the epoxy glue and Blu Tack without harming it and set free.

@@

Adhesion measurements were performed on a custom force measurement
setup developed in-house (Figure \ref{fig:Setup}). A fibre optic
displacement sensor (\emph{Philtec D20, PHILTEC, Inc. USA}) together
with a steel bending beam (spring constant = 68.1 Nm\protect\textsuperscript{-1}) constituted
the vertical force sensor. Beam deflection was calibrated using 4
different known weights to get the corresponding force. A
3D printed substrate holder (22 $\times$ 22 $\times$ 8 mm) was glued to the end of the bending beam.
The holder was designed to enable switching from one substrate to
another without removing any glue. It also had transparent side walls
which allowed us to fill it with water for the underwater experiments
as well as observe the contact. The force sensor was mounted on a stage
consisting of a X-piezo element (\emph{Physik Instrumente, Germany}), used for precise lateral movements. Additionally, a separate Z-piezo element, fixed upright,
was used for vertical up-down motion, bringing the insect in contact
with the substrate from the top. Coarse movements of the bottom stage were done using the XYZ motors (\emph{OWIS GmbH, Germany}).
A coaxial illuminated tube microscope
(\emph{Navitar, USA}) with 2$\times$ objective and a stereo-microscope
with 1$\times$ objective (\emph{Wild Heerbrugg, Switzerland}) fit with digital video cameras 
(\emph{Blackfly S, FLIR, USA}, 2448 $\times$ 2048 px; \emph{Basler ace U, Germany}, 1280 $\times$ 1024 px)
were used to record the sample contact with the substrate from ventral
and side views respectively. Pad contact area was visualised through
the substrate under reflection mode with the help of co-axial illumination. A goniometer was used to adjust the substrate alignment
with the ventral view optics to achieve total internal reflection.
The data acquisition from the force sensor and cameras, together with
the appropriate piezo motion steps were synchronised using a custom
LABVIEW (\emph{National Instruments, USA}) program. Force data was acquired at a sample rate of 984 Hz,
averaged to 512 points per motion step. Videos were recorded at 20
frames per second.

The vertical and lateral piezos were used simultaneously to perform approach-retract
adhesion tests with the substrate to get the pull-off force. However,
instead of a simple down-up motion, an additional 100 \textmu m lateral sliding motion in the proximal direction 
was introduced after the leg made contact, to ensure most of the hair tips align well with the substrate \cite{RN19}.
A further 10 \textmu m compression step (approach) set all hairs in slight compression which helped further contact
with the surface. Next, a short pause (1 s) removed any
viscoelastic effects before finally retracting the leg away from the
substrate. All approach, retract and lateral slide motion was done
at a speed of 62.5 \textmu ms\protect\textsuperscript{-1}. Ventral view video recordings
were used for contact area extraction while the side view imaging
was used to visually aid orienting the pad with the substrate before
a test.

For underwater experiments, 1 ml Milli-Q water was pipetted into the
substrate holder (roughly 3 mm water level). The beetle was then partially 
submerged to allow underwater contact of the pad with the substrate. In order to achieve contact without
a trapped air bubble, the water was first degassed separately in a vacuum chamber
at 10 mbar pressure for 3 hours and then pipetted into the holder immediately. Before the experiments,
the pad was brought into contact with the clean dry surface 10 times repeatedly 
to ensure the hairs are free of any contaminating particles.

Five force measurements were subsequently performed on a fresh spot of the substrate and averaged for data analysis. 
Experiments were repeated five times with unique male beetles for each mode of contact (``\emph{in air}'', (``\emph{underwater:
bubble}'' and (``\emph{underwater: no bubble}'') and substrate (hydrophilic, hydrophobic). Thus, in total, 30 beetles were tested.
%CHECK TYPE OF CONTACT CHANGE TO MODE OF CONTACT%

@@

For measurements in air, the pull-off force was defined as the minimum
negative force during the retraction step (Figure \ref{fig:Setup}).
For underwater measurements, an additional correction was necessary.
When the beetle was partially submerged underwater, its contact line at the
water surface shifted, which influenced the force readout due to surface
tension and buoyancy. This effect needed to be cancelled. So, a ``background''
force data was recorded, where the submerged beetle makes no contact
with the substrate. This background data was then subtracted from
a typical force data with substrate contact to correct for the external
surface tension effects. The pull-off force was subsequently calculated
from the minima as before.

@@

Standard 20 mm wide glass cover-slips were used as the hydrophilic
substrate. Glass was wiped with isopropanol, rinsed in water and dried
under nitrogen flow. For the hydrophobic substrate, the glass cover slip was coated with
a fluorosilane via chemical vapour deposition (CVD). First, the glass
was cleaned using IPA. The surface was then plasma cleaned in a oxygen
plasma chamber (\emph{Femto, Diener Electronic GmbH, Germany}) for 10 min at 120 W. Next, 0.2 ml of
Trichloro(1H,1H,2H,2H-perfluorooctyl) silane (PFOTS), procured from
Sigma Aldrich, was put in a sealed chamber along with the the cleaned
glass. The chamber was placed under 100 mbar pressure for 10 min for
the CVD process. Finally, the substrate was annealed at 150\textcelsius{}
for 3 hours. Henceforth, we refer to the hydrophilic normal glass substrate 
as simply \emph{Glass} and the hydrophobic fluorinated glass substrate as \emph{PFOTS}.

The surface chemistry was characterised by dynamic contact angle
measurements, performed with a contact angle goniometer (\emph{OCA 35, DataPhysics Instruments GmbH, Germany})
The substrate's wetting towards a polar (Milli-Q water) and a non-polar (n-hexadecane) liquid was tested. Advancing
and receding contact angles were measured for a maximum drop volume
of 10 \textmu l and with 0.5 \textmu ls\protect\textsuperscript{-1} flow rate (Table \ref{tab:Contact-Angles}).

\begin{table}[H]
\centering{}%
\begin{tabular}{|c|c|c|c|}
\hline 
Substrate & Liquid & \ensuremath{\theta}\textsubscript{A} & \ensuremath{\theta}\textsubscript{R}\tabularnewline
\hline 
\hline 
\multirow{2}{*}{Glass} & Water & 63\ensuremath{\pm}5\textdegree{} & 20\ensuremath{\pm}2\textdegree{}\tabularnewline
\cline{2-4} \cline{3-4} \cline{4-4} 
 & n-Hexadecane & <10\textdegree{} & <10\textdegree{}\tabularnewline
\hline 
\multirow{2}{*}{PFOTS} & Water & 122\ensuremath{\pm}1\textdegree{} & 93\ensuremath{\pm}2\textdegree{}\tabularnewline
\cline{2-4} \cline{3-4} \cline{4-4} 
 & n-Hexadecane & 88\ensuremath{\pm}2\textdegree{} & 56\ensuremath{\pm}5\textdegree{}\tabularnewline
\hline 
\end{tabular}\caption{Dynamic contact angles (Mean \ensuremath{\pm} SD, n = 3) of Milli-Q water and n-hexadecane on the different test substrates. \label{tab:Contact-Angles}}
\end{table}

%\subsubsection{Field desorption mass spectroscopy}
%
%A previous study on arachnids \cite{RN223} reported that its secreted
%fluid does not dissolve in water. To test whether the beetles retain
%their adhesive fluid underwater unchanged, we performed a Field Desorption Mass Spectroscopy
%(FDMS) using a ZAB 2-SE-FPD spectrometer (VG Instruments). The measurements
%were done on the extracted secretions before and after rinsing its
%legs with water. The middle leg of an Asian ladybird (\emph{Harmonia
%axyridis}) was immersed in 50 \textmu L THF for 20 min and then transferred
%to the measurement chamber of the FDMS. As a reference, pure THF was
%used. The second middle leg of the same ladybird was subsequently
%immersed in 100 \textmu L Milli-Q water for 15 min, then in THF for
%20 min and then transferred to the measurement chamber of the spectrometer.
%Molecular composition was extracted from the peak positions of the
%FDMS spectra.

@@

%\subsubsection{Adhesion measurements}

@@

\begin{figure}[H]
\centering{}\includegraphics[scale=0.5]{Figure2-Expt_effect_of_contact}\caption{\label{fig:Effect-of-contact}Box-and-whisker plot showing
 adhesion force measurements of ladybug beetle's (\emph{Coccinella
septempuctata}) distal pad on glass (blue) and PFOTS (red) substrates in air and underwater
conditions. The two modes of contact during underwater experiments
are represented separately: \textquotedblleft\emph{bubble}\textquotedblright{}
and \textquotedblleft\emph{no bubble}\textquotedblright . Crosses
represent theoretical predictions (see text) of adhesion force, while, circles
represent the contribution of the bubble itself, calculated from the
capillary bridge model. In the model, hair diameter = 4 \textmu m,
pad diameter = 200 \textmu m, hair length = 40 \textmu m,
N\protect\textsubscript{hairs} = 500, V\protect\textsubscript{fluid}
= 4.2 fL and V\protect\textsubscript{bubble} = 1.2 nL. Interfacial
tension of the tarsal adhesive fluid in air and water were assumed to be
24 mNm\protect\textsuperscript{-1} and 48 mNm\protect\textsuperscript{-1} respectively and water surface tension is 72 mNm\protect\textsuperscript{-1}.}
\end{figure}

Apart from the three depicted contact modes, we observed an additional
fourth type which occurred in roughly 25\% of our underwater experiments.
In this scenario, the ventral view recordings show that none of the hairs
appear to contact well with either glass or PFOTS substrate, unlike the other
three contact modes (see supplementary info). This ``bad contact'' scenario shows no adhesion %INCLUDE SUPPLEMENTARY%
with either glass or PFOTS substrate. While it was not completely
clear why such a contact occurs, there can be two possible reasons.
First, the hairs could get bundled due to a small air meniscus within
the hairs, resulting in their disorientation. Second, a thin water
layer at the substrate interface might not be drained out to allow
the hairs to make contact with the substrate, resulting in a loss
of adhesion.

%\subsubsection{Field desorption mass spectroscopy}
%
%FDMS results confirm the presence of adhesive fluid on an Asian ladybird's
%leg when underwater (Table \ref{tab:Molecular-distribution-of}).
%Molecular weights of the secreted fluid mixtures extracted from the
%beetle's leg, without and after immersion in water, show that, except
%for two molecular weights (406.8 g/mol and 331.6 g/mol), the chemical
%fingerprint remained unchanged. This indicates that the adhesion fluid
%was not washed away underwater. Probable compounds in the fluid, corresponding
%to the resultant molecular weights, include mostly aliphatic hydrocarbons
%with traces of aldehydes. Our preliminary measurements on \emph{Harmonia axyridis} gives us confidence
%to assert that, even for the case of \emph{Coccinella
%septempuctata}, the adhesive fluid was not washed away from the hairs during the underwater experiments. 
%
%\begin{table}[H]
%\centering{}%
%\begin{tabular}{|c|c|c|}
%\hline 
%Without rinsing (g/mol) & After rinsing (g/mol) & Probable compounds\tabularnewline
%\hline 
%\hline 
%324.5 & 324.5 & C\textsubscript{23}H\textsubscript{48}, C\textsubscript{22}H\textsubscript{44}O\tabularnewline
%\hline 
% & 331.6 & C\textsubscript{24}H\textsubscript{44}\tabularnewline
%\hline 
%350.5 & 350.5 & C\textsubscript{25}H\textsubscript{50}\tabularnewline
%\hline 
%352.5 & 352.5 & C\textsubscript{25}H\textsubscript{52}, C\textsubscript{24}H\textsubscript{48}O\tabularnewline
%\hline 
%378.5 & 378.5 & C\textsubscript{27}H\textsubscript{54}\tabularnewline
%\hline 
%404.6 & 404.5 & C\textsubscript{29}H\textsubscript{56}\tabularnewline
%\hline 
%406.8 &  & C\textsubscript{29}H\textsubscript{58}\tabularnewline
%\hline 
%432.8 & 432.7 & C\textsubscript{31}H\textsubscript{60}\tabularnewline
%\hline 
%\end{tabular}\caption{Molecular weights of adhesive fluid secretion of \emph{Harmonia axyridis}
%with and without rinsing the beetle's leg in water. \label{tab:Molecular-distribution-of}}
%\end{table}

@@

\begin{figure}[H]
\includegraphics[width=0.7\linewidth]{Figure3-Model_schematic}\caption{\label{fig:Model}The capillary bridge model. The hairs make contact
with the substrate (hydrophilic or hydrophobic) in three ways: a) \emph{In air}, where the tarsal adhesive
fluid bridges are surrounded by air; b) \emph{Underwater: no bubble},
where the tarsal adhesive fluid bridges are fully surrounded by water; c)\emph{
Underwater: bubble}, where part of the tarsal adhesive fluid bridges are
inside the bubble while others are outside in water (see text for details). The corresponding
ventral view contact images of the beetle's pad are shown on the right.}
\end{figure}

@@

Our study provides further validation that capillary forces govern insect adhesion and van der Waals contribution,
if any, must be negligible. Further, the capillary forces can even
enable insect attachment underwater depending on the substrate chemistry.
When underwater, without a trapped bubble, the pads adhere strongly
to a hydrophobic substrate, but poorly to a hydrophilic substrate,
even though it shows similarly strong adhesion to both substrates
in air. This behaviour can only be explained by capillary forces and the wetting properties of the fluid. Our
preliminary FDMS results further provides validation to our assumption
that the adhesive fluid can form capillary bridges with the substrate
in water, instead of getting washed away (Table \ref{tab:Molecular-distribution-of}). %CHANGE REFERENCE!%
